\LARGE \bf Detection of design pattern : A systematic mapping study

### 2015-12-29 article/main.tex
petit ajout sur le process

Introduction goes here

@@

\subsection{subsection1}

subsection

@@

selection process goes here

Exemple d'image

   \begin{figure}[thpb]
      \centering
      \framebox{\parbox{3in}{We suggest that you use a text box to insert a graphic (which is ideally a 300 dpi TIFF or EPS file, with all fonts embedded) because, in an document, this method is somewhat more stable than directly inserting a picture.
}}
      %\includegraphics[scale=1.0]{figurefile}
      \caption{Inductance of oscillation winding on amorphous
       magnetic core versus DC bias magnetic field}
      \label{figurelabel}
   \end{figure}

@@

\bibitem{c1} G. O. Young, ÒSynthetic structure of industrial plastics (Book style with paper title and editor),Ó 	in Plastics, 2nd ed. vol. 3, J. Peters, Ed.  New York: McGraw-Hill, 1964, pp. 15Ð64.
\bibitem{c2} W.-K. Chen, Linear Networks and Systems (Book style).	Belmont, CA: Wadsworth, 1993, pp. 123Ð135.
\bibitem{c3} H. Poor, An Introduction to Signal Detection and Estimation.   New York: Springer-Verlag, 1985, ch. 4.
\bibitem{c4} B. Smith, ÒAn approach to graphs of linear forms (Unpublished work style),Ó unpublished.

>>>>

Introduction goes here
% pourquoi la detection

% pourquoi ce systematic mapping

@@

In this section, we discuss step by step how we conducted our systematic mapping study. We have followed the process defined by Petersen et al \cite{c1}.

\subsection{Research question}

The main goal of this paper is to determine the quantity and trends of research in design pattern detection and the quality of proposed detection methods.
\begin{itemize}
	\item \textbf{RQ1} : How mature is research on the subject of design pattern detection ?
	\item \textbf{RQ2} : What methods of design pattern detection are used ?
\end{itemize}

\subsection{Data source and queries}

We decided to query only one database, Scopus \cite{c2}, that claimed to be the largest abstract and citation database of peer-reviewed literature. It indeed index the main Computer Science databases : Springer, IEEE, ACM and others. The main advantage of doing so is that one could easily export result of an important number of publication from Scopus.

From the two research question we tried to maximise the number of publication found on the subject. To achieve that purpose we used for the query a disjonction of thesaurus for detection on their respective contracted form : detect*, recogni* and ident*. We have then added to the query a disjonction of pattern and motif.
We have limited the query to the abstract, the title, and keywords of each article.

We have limited our research to the year between 2000 and 2015 included.

We have also limited our research to the field of computer science and engineering.

The query resulted of a total of 403 articles. In those articles, we found two duplicates that we have immediately removed from the result.

\subsection{Screening}

After having queried the database, we exported results found and process to screening.

% par paire de deux et resolve conflict

The aim of screening is to select papers relevant to design pattern detection. For that purpose, we used an exclusion scheme containing four criteria :

\begin{enumerate}
	\item \textbf{Not a contribution in software engineering} : %explaination ,
	\item \textbf{Not a full conference or research paper},
	\item \textbf{Not about software design pattern} : %explaination,
	\item \textbf{The main contribution of the paper is not about detection of design pattern} : %explaination
\end{enumerate}

If in article matched more than one criteria, we assigned the lowest criteria to him.

% kappa de cohen

\subsection{Classification scheme}

% comment on l'a choisit

% explication pour chaque catégorie
\begin{itemize}
	\item \textbf{Detection strategy}
	\item \textbf{Language generality}
	\item \textbf{Analysis type}
	\item \textbf{Validation method}
	\item \textbf{Detection Level}
	\item \textbf{Detected pattern types}
	\item \textbf{Pattern detection generality}
\end{itemize}

\subsection{Systematic map}

@@

@@

\bibitem{c1} K. Petersen, R. Feldt, S. Mujtaba, and M. Mattsson, “Systematic mapping studies in software engineering,” in Proc. of the 12th Int. Conf. on Eval. and Asses. in Soft. Eng., ser. EASE’08. Swinton, UK, UK: British Computer Society, 2008.

\bibitem{c2} www.scopus.com
